### 2018-11-30 README.Rmd
add appveyor, rebuild README

---
output:
  md_document:
    variant: markdown_github
---

@@

[![DOI](https://zenodo.org/badge/11856817.svg)](https://zenodo.org/badge/latestdoi/11856817)
[![codecov.io](https://codecov.io/github/ropensci/RNeXML/coverage.svg?branch=master)](https://codecov.io/github/ropensci/RNeXML?branch=master)
[![Build Status](https://api.travis-ci.org/ropensci/RNeXML.png)](https://travis-ci.org/ropensci/RNeXML)
[![Coverage Status](https://img.shields.io/codecov/c/github/ropensci/RNeXML/master.svg)](https://codecov.io/github/ropensci/RNeXML?branch=master)
[![CRAN status](https://www.r-pkg.org/badges/version/RNeXML)](https://cran.r-project.org/package=RNeXML)
![downloads](http://cranlogs.r-pkg.org/badges/grand-total/RNeXML)

>>>>

---
output: github_document
---

@@

[![DOI](https://zenodo.org/badge/11856817.svg)](https://zenodo.org/badge/latestdoi/11856817)
[![Build Status](https://api.travis-ci.org/ropensci/RNeXML.png)](https://travis-ci.org/ropensci/RNeXML)
[![Windows build status](https://ci.appveyor.com/api/projects/status/dhiwp5blx2ns2yba/branch/master?svg=true)](https://ci.appveyor.com/project/cboettig/rnexml/branch/master)
[![CRAN status](https://www.r-pkg.org/badges/version/RNeXML)](https://cran.r-project.org/package=RNeXML)
[![codecov.io](https://codecov.io/github/ropensci/RNeXML/coverage.svg?branch=master)](https://codecov.io/github/ropensci/RNeXML?branch=master)
![downloads](http://cranlogs.r-pkg.org/badges/grand-total/RNeXML)
